Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 conclusions.tex
Adjusted spacing
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1217 ccdd05d5-56c1-461a-bf98-85f6876523b4

Although we have demonstrated a computationally feasible detection statistic
for advance detection, we have not yet explored data calibration and whitening,
triggering, coincidence, and ranking of gravitational wave candidates in a
framework that supports early \EM\ followup.
\begin{comment}
One complication in deploying a
low-latency or early-warning search is that whitening the detector data
involves estimating the noise power spectrum, which is often done acausally.
We will have to look into causal or low latency alternatives to conventional
spectral estimation techniques.  
\end{comment}
We will explore these and also using the time-slice decomposition and the \SVD\
to form low-latency signal-based vetoes (e.g.  $\chi^2$ statistics) that have
been essential for glitch rejection used in previous \GW{} \CBC{} searches.

>>>>

Although we have demonstrated a computationally feasible detection statistic
for advance detection, we have not yet explored data calibration and whitening,
triggering, coincidence, and ranking of gravitational wave candidates in a
framework that supports early \EM\ followup.
\begin{comment}
One complication in deploying a
low-latency or early-warning search is that whitening the detector data
involves estimating the noise power spectrum, which is often done acausally.
We will have to look into causal or low latency alternatives to conventional
spectral estimation techniques.  
\end{comment}
We will explore these and also using the time-slice decomposition and the \SVD\
to form low-latency signal-based vetoes (e.g.~$\chi^2$~statistics) that have
been essential for glitch rejection used in previous \GW{} \CBC{} searches.
